---
classoptions: 
  - sn-nature      
  # - referee       # Optional: Use double line spacing 
  # - lineno        # Optional: Add line numbers
  # - iicol         # Optional: Double column layour
title: "Durably reducing consumption of meat and animal products is an unsolved problem: results from a meta-analysis"
titlerunning: MAP-reduction-meta
authors: 
  - firstname: Seth Ariel
    lastname: Green
    email: setgree@stanford.edu
    affiliation: 1
    corresponding: TRUE
  - firstname: Maya 
    lastname: Mathur
    affiliation: 1
  - firstname: Austin Benny
    lastname: Smith 
    affiliation: 2
affiliations:
  - number: 1
    info:
      orgdiv: Humane and Sustainable Food Lab
      orgname: Stanford University
  - number: 2
    info:
      orgname: Allied Scholars for Animal Protection 
keywords:
  - key
  - dictionary
  - word
abstract: |
  **Purpose**: 
  **Methods:** 
  **Results:** 
  **Conclusion:**
bibliography: "./manuscript/vegan-refs.bib"
output: 
  rticles::springer_article
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.path='results/figures/',
                      out.extra = "")  # This forces knitr to label all figures.

source('./scripts/libraries.R')
source('./scripts/functions.R')
source('./scripts/load-data.R')
source('./scripts/red-and-processed-meat.R')
# final thing is going to look like
# robumeta::robu(d ~ 1, data = dat, studynum = unique_study_id, var.eff.size = var_d, modelweights = "HIER")
```

# Introduction {#sec1}

Demand for meat and animal products (MAP) is increasingly recognized as a major contributor to premature deaths [@willett2019; @landry2023], public health risks [@slingenbergh2004; @graham2008], ecological harms [@greger2010] and climate change [@scarborough2023; @koneswaran2008] as well as an ethical crisis in its own right [@kuruc2023; @singer2023].

Supply-side interventions, such as banning or taxing certain practices or products, risk political backlash if public opinion is not supportive.
It is of vital importance, therefore, to assess which strategies and theoretical perspectives lead to the largest and most durable reductions in demand for MAP products, under which conditions, and for which populations.
This paper answers these questions with a meta-analysis of the MAP reduction studies with the strongest designs, power, and measurement strategies.

The research on diet and its personal, cultural, and practical antecedents on the one hand and its consequences for health, the environment, and animal welfare on the other is vast.
By our count, there have been over one hundred previous reviews on these questions in the past two decades, with at least thirty-seven focused specifically on MAP reduction.
However, two prior investigations revealed three common gaps in the literature: a lack of long-term follow-ups, a preponderance of non-consumption outcomes, and inattention to the potential gap between intentions and what people actually eat [@mathur2021meta; @mathur2021effectiveness].
Our paper puts these issues front and center by exclusively meta-analyzing randomized controlled trials (RCTs) that meet the following inclusion criteria:

-   Intention to reduce overall MAP consumption, rather than (e.g.) encouraging substitution from beef to chicken [@mathur2022ethical];

-   At least 25 subjects each in treatment and control, or, for cluster-randomized trials, at least 10 clusters in total;

-   Measures of MAP consumption, whether self-reported or observed directly, rather than (or in addition to) attitudes, intentions, beliefs or hypothetical choices;

-   Outcomes recorded at least a single day after treatment begins.

Additionally, studies needed to be made publicly available in English by December 2023.

```{r useful_constants, include=F, echo=F}
num_papers <- as.numeric(max(dat$unique_paper_id))
num_studies <- as.numeric(max(dat$unique_study_id))
num_interventions <- as.numeric(nrow(dat))
```

In total we, coded `r num_papers` papers, comprising `r num_studies` separate studies and `r num_interventions` interventions. 

# Results {#sec2}

# Methods {#sec3}

# Discussion {#sec4}

\backmatter

\bmhead{Supplementary information}

\bmhead{Acknowledgments}

# Declarations {.unnumbered}

# Appendix {#secA1}

# Bibliography
