---
classoptions: 
  - sn-nature      
  # - referee       # Optional: Use double line spacing 
  # - lineno        # Optional: Add line numbers
  # - iicol         # Optional: Double column layour
title: "Durably reducing consumption of meat and animal products is an unsolved problem: results from a meta-analysis"
titlerunning: MAP-reduction-meta
authors: 
  - firstname: Seth Ariel
    lastname: Green
    email: setgree@stanford.edu
    affiliation: 1
    corresponding: TRUE
  - firstname: Maya 
    lastname: Mathur
    affiliation: 1
  - firstname: Benny
    lastname: Smith 
    affiliation: 2
affiliations:
  - number: 1
    info:
      orgdiv: Humane and Sustainable Food Lab
      orgname: Stanford University
  - number: 2
    info:
      orgname: Allied Scholars for Animal Protection 
keywords:
  - key
  - dictionary
  - word
abstract: |
  Which theoretical approach leads to the broadest and most enduring reductions in consumptions of meat and animal products (MAP)? We address these questions with a theoretical review and meta-analysis of especially rigorous Randomized Controlled Trials (RCTs). We meta-analyze 33 papers comprising 39 studies,107 interventions, and approximately 78000 subjects. We find that these papers employ either a nudge, norms, or persuasion approach to changing behavior (some papers combine norms and persuasion). Unfortunately, the pooled effect of these interventions on MAP consumption outcomes is just $\Delta$ = 0.0603, suggesting that this is effectively an unsolved problem. Reducing consumption of red and processed meat appears to be an easier target: $\Delta$ = 0.2493, but because of missing data on potential substitution to other MAP, we can’t say anything definitive about the consequences of these interventions on animal welfare. We further explore heterogeneity by approach, population, and study features. We conclude that while no theoretical approach provides a proven remedy to MAP consumption, research has generally been getting more rigorous over time, and many promising approaches remain untested.
bibliography: "./manuscript/vegan-refs.bib"
output: 
  rticles::springer_article
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.path='results/figures/',
                      out.extra = "")  # This forces knitr to label all figures.

source('./scripts/libraries.R')
source('./scripts/functions.R')
source('./scripts/load-data.R')
source('./scripts/red-and-processed-meat.R')
```

# Introduction {#sec1}

Consumption of meat and animal products (MAP) is increasingly recognized as a major contributor to premature deaths [@willett2019; @landry2023], public health risks [@slingenbergh2004; @graham2008], ecological harms [@greger2010] and climate change [@scarborough2023; @koneswaran2008] as well as an ethical crisis in its own right [@kuruc2023; @singer2023].

Supply-side interventions, such as banning or taxing certain practices or products, risk political backlash if they do not have broad public support.
It is of vital importance, therefore, to assess which strategies and theoretical perspectives lead to the largest and most durable reductions in demand for MAP products, under which conditions, and for which populations.
We address these questions with a meta-analysis of the most rigorous studies aimed at reducing MAP consumption.

The research on diet and its personal, cultural, and practical antecedents on the one hand and its consequences for health, the environment, and animal welfare on the other is vast.
By our count, there have been at least 118 previous reviews on these questions in the past two decades, with at least thirty-seven focused specifically on MAP reduction.
However, comparatively few of these are quantitative, and most prior reviews investigated particular approaches, for example choice architecture [@bianchi2018restructuring], appeals to animal welfare [@mathur2021effectiveness], or literacy interventions [@DiGennaro2024], rather than comparing approaches to one another.
Moreover, two prior investigations revealed three common gaps in the MAP literature: a dearth of long-term follow-ups, consumption outcomes, and inattention to the gap between intentions and behavior [@mathur2021meta; @mathur2021effectiveness].

Our paper addresses these concerns by meta-analyzing randomized controlled trials (RCTs) that

-   were designed to voluntarily reduce MAP consumption, rather than (e.g.) encouraging substitution from red to white meat or fish or removing meat from someone's plate

-   had least 25 subjects each in treatment and control, or, for cluster-randomized trials, at least 10 clusters in total;

-   measured MAP consumption, whether self-reported or observed directly, rather than (or in addition to) attitudes, intentions, beliefs or hypothetical choices;

-   recorded outcomes at least a single day after the start of treatment.

Additionally, studies needed to be publicly circulated by December 2023 and published in English.

```{r useful_constants, include=F, echo=F}
num_papers <- as.numeric(max(dat$unique_paper_id))
num_studies <- as.numeric(max(dat$unique_study_id))
num_interventions <- as.numeric(nrow(dat))
n_total <-  plyr::round_any(x = sum(dat$n_c_total_pop) + sum(dat$n_t_total_pop), 1000, floor)

RPMC_papers <- as.numeric(max(RPMC$unique_paper_id))
RPMC_studies <- as.numeric(max(RPMC$unique_study_id))
RPMC_interventions <- as.numeric(nrow(RPMC))
n_meat_total <-  plyr::round_any(x = sum(RPMC$n_c_total_pop) + sum(RPMC$n_t_total_pop), 1000, floor)

decade_tab <- dat |> group_by(unique_paper_id) |>  slice(1) |>  ungroup() |> count(decade)
```

We coded `r num_papers` papers [@abrahamse2007; @alblas2023; @aldoh2023; @allen2002; @andersson2021; @acharya2004; @berndsen2005; @bertolaso2015; @bianchi2022; @bochmann2017; @bschaden2020; @carfora2023; @coker2022; @cooney2016; @fehrenbach2015; @feltz2022; @griesoph2021; @haile2021; @hatami2018; @hennessy2016; @jalil2023; @lacroix2020; @mathur2021effectiveness; @mattson2020; @merrill2009; @norris2014; @peacock2017; @piester2020; @polanco2022; @sparkman2017; @sparkman2020; @sparkman2021; @weingarten2022] comprising `r num_studies` separate studies, `r num_interventions` interventions, and approximately `r n_total` subjects.
(Some treatments were administered at the level of day or cafeteria and did not record their number of human subjects.) The earliest paper was published in 2002 [@allen2002], and a majority (`r decade_tab$n[3]` of `r num_papers`) have been published since 2020.

We also coded a supplementary dataset of `r RPMC_papers` papers aimed at reducing, and measuring, consumption of red and/or processed meat (RPM) [@carfora2017correlational; @carfora2017randomised; @carfora2019; @carfora2019informational; @delichatsios2001; @dijkstra2022; @emmons2005cancer; @emmons2005project; @jaacks2014; @james2015; @lee2018; @perino2022; @schatzkin2000; @sorensen2005], comprising `r RPMC_studies` studies, `r RPMC_interventions` interventions, and approximately `r n_meat_total` subjects.
Last, we compiled a third dataset of 782 excluded studies, along with their reason(s) for exclusion.

# Results {#sec2}

## Three theoretical categories: persuasion, choice architecture, and norms {#sec2.1}

```{r table_one, echo=F, message=F}
library(kableExtra)
source('./functions/meta_result_formatter.R')

mr <- meta_result_formatter

# Overall
model <- dat |> map_robu()

# Nudge
nudge_model <- dat |> filter(theory == 'nudge') |> map_robu()
nudge_n <- dat |> filter(theory == 'nudge') |> 
  summarise(n_total = round_any(sum(n_t_total_pop + n_c_total_pop), 100, floor))
# Norms
norms_model <- dat |> filter(theory == 'norms') |> map_robu()
norms_n <- dat |> filter(theory == 'norms') |>
    summarise(n_total = round_any(sum(n_t_total_pop + n_c_total_pop), 100, floor))

# Norms + Persuasion
norms_persuasion_model <- dat |> filter(theory == 'norms & persuasion') |> map_robu()

norms_pers_n <-  dat |> filter(theory == 'norms & persuasion')|>
  summarise(n_total = round_any(sum(n_t_total_pop + n_c_total_pop), 100, floor))

# Persuasion Overall
persuasion_model <- dat |> filter(theory == 'persuasion') |> map_robu()

persuasion_n <- dat |> filter(theory == 'persuasion') |>
  summarise(n_total = round_any(sum(n_t_total_pop + n_c_total_pop), 100, floor))

# Table One
table_one <- tibble(
  Approach = c("\\textbf{Overall}", "Norms", "Nudge",
               "Persuasion", "Norms + Persuasion"),
  "N (Studies)" = c(model$N_studies, norms_model$N_studies, 
                    nudge_model$N_studies, persuasion_model$N_studies,
                    norms_persuasion_model$N_studies),
  "N (Interventions)" = c(model$N_interventions, norms_model$N_interventions,
                          nudge_model$N_interventions, 
                          persuasion_model$N_interventions,
                          norms_persuasion_model$N_interventions),
  "N (subjects)" = c(n_total, norms_n, nudge_n, persuasion_n, norms_pers_n),
  "Glass's $\\Delta$ (SE)" = c(mr(model), mr(norms_model),
                               mr(nudge_model), mr(persuasion_model), 
                               mr(norms_persuasion_model))) |> 
  kable(format = "latex", booktabs = TRUE, escape = FALSE,
        caption = "Norm, Nudge, and persuasion approaches to MAP reduction",
        label = "tab:table_one") |>
  kable_styling(latex_options = "hold_position") |>
  footnote(general_title = "",
           general = "* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001", 
           escape = FALSE)
table_one

# Persuasion (Health)
health_model <- dat |> filter(str_detect(secondary_theory, 'health')) |> map_robu()

# Persuasion (Environment)
environment_model <- dat |> filter(str_detect(secondary_theory, 'environment')) |> map_robu()

# Persuasion (Animal Welfare)
animal_model <- dat |> filter(str_detect(secondary_theory, 'animal')) |> map_robu()

# Table Two
table_two <- tibble(
  "Persuasion Approach" = c("Health", "Environment", "Animal Welfare"),
  "N (Studies)" = c(health_model$N_studies, 
                    environment_model$N_studies,
                    animal_model$N_studies),
  "N (Interventions)" = c(health_model$N_interventions, 
                          environment_model$N_interventions,
                          animal_model$N_interventions),
  "Glass's $\\Delta$ (SE)" = c(mr(health_model), 
                               mr(environment_model), 
                               mr(animal_model))
) |> 
  kable(format = "latex", booktabs = TRUE, escape = FALSE,
        caption = "Three types of persuasion",
        label = "tab:table_two") |>
  kable_styling(latex_options = "hold_position") |>
  footnote(general_title = "", 
           general = "* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001.", 
           escape = FALSE)
table_two
```

Studies in our database pursued one or more of three main theories of change: norms, nudges, and persuasion, or a combination of norms and persuasion.
Table 1 reports the distribution of studies, interventions, and subjects (approximately) per approach.

**Norms** studies manipulate perceptions of the popularity of desired outcomes, e.g. plant-based dishes [@sparkman2021] or using re-usable mugs[@loschelder2019].
Norms might be descriptive ("33% of British people...successfully engaged in one or more...behaviours to eat less meat" [@aldoh2023]), injunctive (a message with a frowning face for subjects who eat more meat than the average person in their country [@alblas2023]), or dynamic, i.e. they tell subjects that the number of people engaging in desired behavior is increasing [@aldoh2023; @coker2022; @sparkman2017; @sparkman2020; @sparkman2021].
With regards to MAP reduction, this is a comparatively young literature, with the first paper appearing in 2017.

**Persuasion** studies appeal directly to people about eating less meat.
These studies formed the majority of our database.
Arguments typically focus on health [@lacroix2020], the environment [@carfora2023] \textemdash typically climate change \textemdash and animal welfare [@haile2021].
Some are designed to be emotionally activating, e.g. presenting upsetting footage of factory farms [@bertolaso2015], while others present facts more dispassionately, e.g. about the relationship between diet and cancer [@hatami2018].
Many persuasion studies combine arguments, e.g. a leaflet with information in all three categories [@hennessy2016].

Table 2 displays the distribution of persuasion studies within the three categories.
(Note that because many studies present more than one category of message, the number of studies and interventions will sum to more than the total number of persuasion studies and interventions.)

Finally, a handful of studies combines **norms and persuasion** approaches [@hennessy2016; @carfora2023; @lacroix2020; @mattson2020; @piester2020].
These interventions typically suggest reasons to eat less meat side by side with information about changing consumer habits in society.

## An overall small effect {#sec2.2}

Our overall meta-analytic effect size is $\Delta$ = `r model$Delta` (SE = `r model$se`), p = `r model$pval`.
The aggregate effect is statistically significant, but does not indicate a meaningful reduction.

Figure 1 displays the distribution of effect sizes, grouped by paper, with each individual point representing an intervention.
The overall effect size is plotted at the bottom.

```{r forest_plot_nulls_and_cis_}
source('./scripts/forest-plot.R')
print(forest_plot)

effect_size_table <- dat |> sum_tab(neg_null_pos)

significant_CIs <- dat |> select(author, year, d, se_d, neg_null_pos) |>
  mutate(lower_bound = d - (1.96 * se_d),
         upper_bound = d + (1.96 * se_d)) |>
  filter(lower_bound < 0 & upper_bound < 0 |
           lower_bound > 0 & upper_bound > 0) |> 
  mutate(direction = case_when
         (lower_bound > 0 ~ 1,
           upper_bound < 0 ~ 0))
```

This small effect may surprise readers of previous reviews, which typically found more positive results [@mathur2021meta; @meier2022; @chang2023].We attribute this difference to our stricter inclusion criteria.
For instance, of the ten largest effect sizes recorded in [@mathur2021effectiveness], nine were non-consumption outcomes and the tenth came from a non-randomized design.
([@bianchi2018conscious] also found effects on intentions and attitudes but no evidence of effects on behavior.)

As told by the papers in our dataset, `r effect_size_table['0']` of `r num_interventions` interventions had null effects.
However, many studies present a wide variety of outcomes, or include MAP reduction as one of many components of a broader program of behavior change, and focus on their significant results.
`r english::Words(nrow(significant_CIs))` interventions have 95% confidence intervals that do not overlap with zero, `r words(sum(significant_CIs$direction))` of which are positive effects, out of `r nrow(dat)` interventions.

We find some evidence of publication bias in our dataset.
$\Delta$ and standard error are positively correlated, though not significantly.
Further as we see in table 3, the pooled effect size of interventions published in peer-reviewed journals is about 9 times larger than the equivalent effect size in student theses, while interventions published by advocacy organizations produce a small backlash effect on average.

```{r pbulication_bias_checks_to_verify, message=F, include=F, echo=F}

# "$\Delta$ and standard error are positively correlated, though not significantly"
dat |> sum_lm(d, se_d)
# a la the contact hypothesis re-evaluated, the implication here is that an infinitely powered
# study would have an effect size of 0.0008

# within journal articles? 
dat |> filter(pub_status == 'Journal article') |> sum_lm()
# A visual exploration:
dat |>
  ggplot(aes(x = se_d, y = d)) +
  geom_point(size = 3, aes(color = theory, shape = pub_status)) +
  stat_smooth(method = 'lm', se = FALSE) +
  scale_color_manual(values = c("norms" = "blue",
                                "norms & persuasion" = "red",
                                "nudge" = "green",
                                "persuasion" = "purple"
                                )) +
  labs(x = "Standard Error") +
  theme_minimal()
```

```{r table_three, echo=F}
table_three <- dat |> 
  split(~pub_status) |> 
  map(map_robu) |> 
  map(~ .x |> mutate("Glass's $\\Delta$ (SE)" =
                       meta_result_formatter(.x))) |> 
  bind_rows(.id = 'Publication status') |> 
  mutate(`Publication status` = case_when(
    `Publication status` == "advocacy_org" ~ "Advocacy Organization",
    TRUE ~ `Publication status`
  )) |>
  rename(
    `N (Studies)` = N_studies,
    `N (Interventions)` = N_interventions) |>
 select(-c(Delta, se, pval))  |> 
  kable(format = "latex", booktabs = TRUE, escape = FALSE,
        caption = "Difference in effect size by publication status",
        label = "tab:table_two") |> 
  kable_styling(latex_options = "hold_position") |>
  footnote(general_title = "",
           general = "* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001.",
           escape = FALSE)
table_three
```

## Red and Processed Meat is an easier target

```{r RPMC_model, echo=F}
# ok this won't be a table
rpmc_model <- RPMC |> map_robu()

# table_three <- tibble(
#   "N (Studies)" = rpmc_model$N_studies,
#   "N (Interventions)" = rpmc_model$N_interventions,
#   "Glass's $\\Delta$ (SE)" = mr(rpmc_model)) |> 
#   kable(format = "latex", booktabs = TRUE, escape = FALSE,
#         caption = "Meta-analytic results for red and processed meat",
#         label = "tab:table_three") |>
#   kable_styling(latex_options = "hold_position") |>
#   footnote(general_title = "", 
#            general = "* p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001", 
#            escape = FALSE)
# table_three
```

On average, interventions aimed at reducing consumption of red and processed meat are considerably more effective than MAP reduction interventions are: $\Delta$ = `r rpmc_model$Delta` \text{(SE = `r rpmc_model$se`)}, p = `r rpmc_model$pval`.
Each of these studies employs persuasion, and a majority (16/19) appeal to personal health.
Moreover, many of these interventions are aimed at older people who have had serious health issues, e.g. cancer survivors [@lee2018; @james2015].

However, the effect of these interventions on MAP reduction *overall* is unknown because these studies do not report on consumption of white meat and/or fish.
Red meat is of special concern for its environmental and health consequences [@grummon2023], but chicken is arguably worse for animals on a pound-for-pound basis [@mathur2022ethical].
For some plausible patterns of substitution, these interventions are a net positive for personal health and the environment but a net negative for animal welfare.

## Norms work sometimes, but it is not clear why or when

```{r include=F, echo=F}
norms_overall_model <- dat |> filter(str_detect(theory, "norms")) |> map_robu()

# look at the distribution of effect sizes

dat |> filter(str_detect(theory, "norms")) |> select(author, year, theory, d, se_d, intervention_condition, neg_null_pos) |> arrange(neg_null_pos, d) |> print(n = 30)

```

The overall effect for intervention with a norms component is $\Delta$ = `r norms_overall_model$Delta` (SE = `r norms_overall_model$se`), p = `r norms_overall_model$pval`.
[INSERT THREE SENTENCES ABOUT NULLS AND NEGATIVES AND BACKLASHES WITHIN A SINGLE STUDYs]

## The evidence for nudges on MAP consumption is scant

Although nudges are common in the diet literature writ large [@olafsson2024; @cadario2020; @szaszi2018], only one study that focused on MAP reduction met our inclusion criteria [@andersson2021].
That study manipulated the salience of a plant-based dish by varying its placement on a menu in a university cafeteria in Sweden.
Placing a plant-based dish at the top of the menu encouraged a decline in sales of the meat-based option, although most people then chose fish over the vegetarian option.
When this pattern is accounted for, the remaining effect is $\Delta$ = `r nudge_model$Delta` (SE = `r nudge_model$se`).

## Health appeals are generally moderately effective, especially when aimed at older, sicker people

## Environmental appeals, especially those aimed at college students, have moderate positive effects

## Animal welfare appeals are almost always ineffective

Di Gennaro also finds null results on animals

## Heterogeneity by country, self-reporting, cluster assignment, delivery method

## These studies are often underpowered to detect effects they actually find

-   X studies do power calculations, and Y of those find results smaller than they're looking for,
-   they also plan effect sizes based on recruited sample rather than follow-up
-   plan for small effects and attrition

## Open science practices are associated with marginally larger effect sizes

# Methods {#sec3}

-   Search
-   Coding
-   Meta-analysis

# Discussion {#sec4}

-   in this article, we
-   we are enocuraged by increasing rigor
-   we look forward to seeing

\backmatter

\bmhead{Supplementary information}

\bmhead{Acknowledgments}

# Declarations {.unnumbered}

# Appendix {#secA1}

A LOT will go here

### Nudge lit is a mses

Theory; behavior change is just hard <https://www.nature.com/articles/s44159-024-00305-0> & most interventions don't work <https://www.bu.edu/bulawreview/files/2023/12/STEVENSON.pdf>

but nudges claim to work – so what's going on?
well, publication bias in nudge studies <https://www.pnas.org/doi/full/10.1073/pnas.2200300119> , it's easier to change beliefs <https://www.aeaweb.org/articles?id=10.1257/jel.20211658> (Effect Sizes on Beliefs versus Behavior), nudges don't scale <https://onlinelibrary.wiley.com/doi/full/10.3982/ECTA18709>

"our read is quite different' <https://www.pnas.org/doi/10.1073/pnas.2200732119> automatacity is not the way forward

# Bibliography

# References

```{r cleanup, echo=F}
unlink("MAP-reduction-meta_files", recursive = TRUE)
```
