---
title: "Meaningfully reducing consumption of meat and animal products is an unsolved problem: results from a meta-analysis"
titlerunning: MAP-reduction-meta
author: 
  - Seth Ariel Green
  - Maya Mathur
  - Benny Smith
date: "`r Sys.Date()`"
output:
  beamer_presentation:
bibliography: './vegan-refs.bib'
header-includes:
  - \usepackage{booktabs}
editor_options:
  chunk_output_type: console
nocite: |
  @aldoh2023, @allen2002, @alblas2023, @coker2022, @griesoph2021, @piester2020, @sparkman2017, @sparkman2020, @andersson2021, @kanchanachitra2020, @bochmann2017, @bschaden2020, @cooney2016, @feltz2022, @haile2021, @mathur2021effectiveness, @peacock2017, @polanco2022, @sparkman2021, @abrahamse2007, @acharya2004, @berndsen2005, @bertolaso2015, @bianchi2022, @fehrenbach2015, @hatami2018, @jalil2023, @merrill2009, @norris2014, @weingarten2022, @carfora2023, @hennessy2016, @mattson2020
---

```{r setup, include=FALSE}
# so that knitr labels figures
knitr::opts_chunk$set(
	fig.path = "../results",
	echo = FALSE,
	out.extra = ""
)
# so we can put the manuscript stuff in its own folder
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(rprojroot::find_rstudio_root_file())

source('./scripts/libraries.R')
source('./scripts/functions.R')
source('./scripts/load-data.R')
source('./scripts/red-and-processed-meat.R')
source('./scripts/models.R')
source('./scripts/tables.R')
source('./scripts/figures.R')
```

## Paper in a nutshell

Meta-analysis of randomized controlled trials (RCTs) that

-   were designed to voluntarily reduce consumption of meat and animal products (MAP), rather than (e.g.) encouraging substitution from red to white meat or fish or removing meat from someone's plate

-   had least 25 subjects each in treatment and control, or, for cluster-randomized trials, at least 10 clusters in total;

-   measured MAP consumption, whether self-reported or observed directly, rather than (or in addition to) attitudes, intentions, beliefs or hypothetical choices;

-   recorded outcomes at least a single day after the start of treatment

## Three Theoretical Categories: Persuasion, Choice Architecture, and Norms

-   Nudges (choice architecture/behavioral economics)
-   Norms ('veggie burgers are a popular choice'/'veggie burgers are becoming more popular')
-   Persuasion approaches:
    -   Appeals to animal welfare
    -   Appeals to health
    -   Appeals to the environment
-   A few studies combined persuasion with norms

## Distribution of approaches:

```{r table_one}
table_one |> kableExtra::kable_styling(font_size = 7) 
```

## Distribution of persuasion interventions:

```{r table_two}
table_two |> kableExtra::kable_styling(font_size = 7)
```

## An Overall Small Effect

-   Meta-analytic average: $\Delta$ = `r model$Delta` (SE = `r model$se`), p = `r model$pval`.
-   Statistically significant but not indicating meaningful reduction
    -   Caveat that 'meaningful' depends on context

## Forest plot

```{r forest_plot, out.width="90%"}
forest_plot
```

## Moderate Evidence of Publication Bias

-   Tests for publication bias:
    -   $\Delta$ and SE positively correlated (not significant).
    -   Studies with pre-analysis plans or openly available data show smaller, non-significant effects.
    -   Peer-reviewed journal interventions show larger effect sizes

```{r table_three}
table_three |> kableExtra::kable_styling(font_size = 7) 
```

## Red and Processed Meat is an Easier Target

-   Red and Processed Meat (RPM) reduction interventions outperform general MAP interventions: $\Delta$ = `r rpmc_model$Delta` (SE = `r rpmc_model$se`), p = `r rpmc_model$pval`.
-   Focus primarily on health benefits.
-   Lacking data on substitution to white meat annd fish.

## Norms Work Sometimes, But unclear when or where

```{r include=F, echo=F}
norms_overall_model <- dat |> filter(str_detect(theory, "norms")) |> map_robust()

# look at the distribution of effect sizes

norms_studies <- dat |> filter(str_detect(theory, "norms")) |> select(author, year, theory, d, se_d, intervention_condition, neg_null_pos) |> arrange(neg_null_pos, d) |> print(n = 30)

norms_proportions  <- norms_studies |>
  sum_tab(neg_null_pos)
```

-   Overall effect for norms interventions: $\Delta$ = `r norms_overall_model$Delta` (SE = `r norms_overall_model$se`), p = `r norms_overall_model$pval`.
-   Wide variability in outcomes, including some backlashes.
-   Unclear limiting principles for when norms work or for whom.
-   see Sparkman et. al (2020) for standout example

## The Evidence for Nudges on MAP Consumption Is Scant

-   Nudge and diet studies is a huge literature...
-   but only two nudge studies met our inclusion criteria.
-   Both showed moderate effect sizes (think a few percentage points change).

## Health Studies Work Better for Red and Processed Meat (RPM) Than for MAP

```{r health_studies, echo=F, include=F}
health_studies <- dat |> 
  filter(str_detect(secondary_theory, 'health')) |> 
  select(author, year, secondary_theory, d, se_d, 
         self_report, neg_null_pos) |> 
  arrange(neg_null_pos, d) |> print(n = 30)

health_proportions <- 
  health_studies |> sum_tab(neg_null_pos)

RPM_health_model <- RPMC |>  
  filter(str_detect(secondary_theory, 'health')) |> map_robust()

# health studies form the majority of RPM studies
RPM_health_numbers <- RPMC |> mutate(health_component = if_else(str_detect(secondary_theory, 'health'), T,F)) |> 
  sum_tab(health_component)
```

Health studies produce an average effect of$\Delta$ = `r health_model$Delta` (SE = `r health_model$se`), p = `r health_model$pval`.
- More effective at reducing RPM than MAP: $\Delta$ = `r RPM_health_model$Delta` (SE = `r RPM_health_model$se`), p = `r RPM_health_model$pval`.

## Environmental Appeals Have Modest Positive Effects

Environmental studies produce an average effect of $\Delta$ = `r environment_model$Delta` (SE = `r environment_model$se`), p = `r environment_model$pval`.
- Strongest evidence from a study on student dining behavior (Jalil et al.2023) which replaced an intro econ lecture for students at a small liberal arts college with a lecture on the environmental and health reasons to cut back on meat -- and then tracked student dining choices for three years - Overall reduction of 5.4%

## Animal Welfare Appeals Are Almost Always Ineffective

```{r animal_welfare_studies, include=F}
animal_proportions  <- dat |> filter(str_detect(secondary_theory, 'animal')) |>
  sum_tab(neg_null_pos)

animal_proportions['0']

neg_animal_results <- dat |> filter(str_detect(secondary_theory, 'animal')) |> filter(d<0) |> count()

advocacy_model <- dat |> filter(advocacy_org != 'N') |> map_robust()
```

-   Pooled effect size for animal welfare appeals: $\Delta$ = `r animal_model$Delta` (SE = `r animal_model$se`), p = `r animal_model$pval`.
-   A full `r animal_proportions['0']` of `r animal_model$N_interventions` interventions in this category are self-described nulls.
-   Slightly more than half (`r neg_animal_results` of `r animal_model$N_interventions`) lead to increases in MAP consumption, though just one of these effects is statistically significant.

## Moderators:

-   No meaningful difference by self-reported outcomes or not
-   nor by how treatment was assigned
-   nor by delay
-   All of these were surprising to me

## some differences by delivery method...

```{r table_four}
table_four|> kableExtra::kable_styling(font_size = 7) 
```

## And region

```{r table_five}
table_five |> kableExtra::kable_styling(font_size = 6.5) 
```

## Conclusions

-   Basically no theory has a really robust evidence base :(

-   Lots of promising interventions haven't been tested yet – still lots of low-hanging fruit!

-   Overall research is getting more rigorous over time – most of these studies have been published since 2020 (the earliest was 2002)

## Thanks! Questions?

-   code and data at <https://github.com/setgree/vegan-meta>
-   my email is [setgree\@stanford.edu](mailto:setgree@stanford.edu){.email}

## Database of studies: {.allowframebreaks}

\bibliography{./vegan-refs.bib}
