---
# Supported options: 
#   sn-nature:       Style for submissions to Nature Portfolio journals
#   sn-basic:        Basic Springer Nature Reference Style/Chemistry Reference Style
#   sn-mathphys:     Math and Physical Sciences Reference Style
#   sn-aps:          American Physical Society (APS) Reference Style
#   sn-vancouver:    Vancouver Reference Style
#   sn-apa:          APA Reference Style 
#   sn-chicago:      Chicago-based Humanities Reference Style
#   default:         Default

classoptions: 
  - sn-basic      
  # - Numbered      # Optional: Use numbered references instead of namedate references (only for sn-nature, sn-basic, sn-vancouver, sn-chicago, sn-mathphys or sn-nature)
  # - referee       # Optional: Use double line spacing 
  # - lineno        # Optional: Add line numbers
  # - iicol         # Optional: Double column layour

title: Durably reducing consumption of meat and animal products is an unsolved problem: results from a meta-analysis
titlerunning: MAP-reduction-meta

authors: 
  - prefix: Dr.
    firstname: Seth Ariel
    lastname: Green
    naturename: imaboss
    degrees: MA
    email: setgree@stanford.edu
    affiliation: 1
    corresponding: TRUE

  - prefix: Dr.
    firstname: Maya 
    lastname: Mathur
    naturename: PIextraordinaire
    degrees: PhD
    email: mmathur@stanford.edu
    affiliation: 1

  - firstname: Austin Benny
    lastname: Smith 
    affiliation: 2


affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: Humane and Sustainable Food Lab
      orgname: Stanford University
    address:
        street: 300 Pasteur Dr
        city: Palo Alto
        postcode: 94304
        state: CA 
        country: USA
  - number: 2
    corresponding: TRUE
    info:
      orgdiv: Allied Scholars for Animal Protectgion
      orgname: 
    address:
        street: 1401 Lavaca St Unit 395
        city: Austin
        postcode: 78701
        state: TX 
        country: USA
    
  
keywords:
  - key
  - dictionary
  - word
  
pacs: 
  jel:
    - "D8"
    - "H51"
  msc:
    - "35A01"
    - "65L10"

# Sample for structured abstract
abstract: |
  **Purpose**: 

  **Methods:** 

  **Results:** 

  **Conclusion:**

bibliography: ./manuscript/vegan-refs.bib

header-includes: |
  %% Per the spinger doc, new theorem styles can be included using built in style, 
  %% but it seems the don't work so commented below
  %\theoremstyle{thmstyleone}%
  \newtheorem{theorem}{Theorem}%  meant for continuous numbers
  %%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
  %% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
  \newtheorem{proposition}[theorem]{Proposition}%
  %%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

  %% \theoremstyle{thmstyletwo}%
  \theoremstyle{remark}
  \newtheorem{example}{Example}%
  \newtheorem{remark}{Remark}%

  %% \theoremstyle{thmstylethree}%
  \theoremstyle{definition}
  \newtheorem{definition}{Definition}%

output: rticles::springer_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.extra = "")  # This forces knitr to label all figures.
```

# Introduction {#sec1}

Demand for meat and animal products (MAP) is increasingly recognized as a major contributor to premature deaths [@willett2019; @landry2023], public health risks [@slingenbergh2004; @graham2008], ecological harms [@greger2010] and climate change [@scarborough2023; @koneswaran2008; @goodland2009], as well as an ethical crisis in its own right

# Results {#sec2}

# Figures {#sec6}

As per the \LaTeX\ standards you need to use eps images for \LaTeX\ compilation and `pdf/jpg/png` images for `PDFLaTeX` compilation. 
Use the `dev` knitr option to use the appropriate format. 
This is one of the major difference between \LaTeX\ and `PDFLaTeX`.
Each image should be from a single input .eps/vector image file. 
Avoid using subfigures.
The command for inserting images for \LaTeX\ and `PDFLaTeX` can be generalized. 
The package used to insert images in `LaTeX/PDFLaTeX` is the graphicx package. 
Figures can be inserted via the normal figure environment as shown in the below example:

```{r fig1, fig.cap = "This is an example of a caption", fig.width = 5}
plot(pressure)
```

# Algorithms, Program codes and Listings {#sec7}

Packages `algorithm`, `algorithmicx` and `algpseudocode` are used for setting algorithms in \LaTeX\ using the format:

```
\begin{algorithm}
\caption{<alg-caption>}\label{<alg-label>}
\begin{algorithmic}[1]
. . .
\end{algorithmic}
\end{algorithm}
```

You may refer above listed package documentations for more details before setting `algorithm` environment. For program codes, the "program" package is required and the command to be used is `\begin{program}` `...` `\end{program}`. A fast exponentiation procedure:

Similarly, for `listings`, use the `listings` package. `\begin{lstlisting}` `...` `\end{lstlisting}` is used to set environments similar to `verbatim` environment. Refer to the `lstlisting` package documentation for more details.

A fast exponentiation procedure:

```{=latex}
\lstset{texcl=true,basicstyle=\small\sf,commentstyle=\small\rm,mathescape=true,escapeinside={(*}{*)}}
\begin{lstlisting}
begin
  for $i:=1$ to $10$ step $1$ do
      expt($2,i$);  
      newline() od                (*\textrm{Comments will be set flush to the right margin}*)
where
proc expt($x,n$) $\equiv$
  $z:=1$;
  do if $n=0$ then exit fi;
     do if odd($n$) then exit fi;                 
        comment: (*\textrm{This is a comment statement;}*)
        $n:=n/2$; $x:=x*x$ od;
     { $n>0$ };
     $n:=n-1$; $z:=z*x$ od;
  print($z$). 
end
\end{lstlisting}
```

```{=latex}
\begin{algorithm}
\caption{Calculate $y = x^n$}\label{algo1}
\begin{algorithmic}[1]
\Require $n \geq 0 \vee x \neq 0$
\Ensure $y = x^n$ 
\State $y \Leftarrow 1$
\If{$n < 0$}\label{algln2}
        \State $X \Leftarrow 1 / x$
        \State $N \Leftarrow -n$
\Else
        \State $X \Leftarrow x$
        \State $N \Leftarrow n$
\EndIf
\While{$N \neq 0$}
        \If{$N$ is even}
            \State $X \Leftarrow X \times X$
            \State $N \Leftarrow N / 2$
        \Else[$N$ is odd]
            \State $y \Leftarrow y \times X$
            \State $N \Leftarrow N - 1$
        \EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}
```

:::: {.minipage latex="{\hsize}"}
\lstset{frame=single,framexleftmargin=-1pt,framexrightmargin=-17pt,framesep=12pt,linewidth=0.98\textwidth,language=pascal}
<!-- Set your language (you can change the language for each code-block optionally) -->
<!-- Start your code-block -->
::: {.lstlisting latex=true}
for i:=maxint to 0 do
begin
{ do nothing }
end;
Write('Case insensitive ');
Write('Pascal keywords.');
:::
::::

# Cross referencing {#sec8}

Figures and tables are labeled with a prefix (fig or tab, respectively) plus the chunk label. 
Other environments such as equation and align can be labelled via the `\label{#label}` command inside or just below the `\caption{}` command.
You can then use the label for cross-reference. As an example, consider
the chunk label declared for Figure\ \ref{fig:fig1} which is
fig1. 
To cross-reference it, use the command
`Figure \ref{fig:fig1}`, for which it comes up as
"Figure\ \ref{fig:fig1}".

To reference line numbers in an algorithm, consider the label declared for the line number 2 of Algorithm\ \ref{algo1} is `\label{algln2}`. To cross-reference it, use the command `\ref{algln2}` for which it comes up as line\ \ref{algln2} of Algorithm\ \ref{algo1}.

## Details on reference citations {#subsec7}

For citations of references, use\ @bib1 or [@bib2]. 


# Methods {#sec11}

# Discussion {#sec12}

Discussions should be brief and focused. In some disciplines use of Discussion or 'Conclusion' is interchangeable. It is not mandatory to use both. Some journals prefer a section 'Results and Discussion' followed by a section 'Conclusion'. Please refer to Journal-level guidance for any specific requirements.

# Conclusion {#sec13}

Conclusions may be used to restate your hypothesis or research question, restate your major findings, explain the relevance and the added value of your work, highlight any limitations of your study, describe future directions for research and recommendations.

In some disciplines use of Discussion or 'Conclusion' is interchangeable. It is not mandatory to use both. Please refer to Journal-level guidance for any specific requirements.

\backmatter

\bmhead{Supplementary information}

If your article has accompanying supplementary file/s please state so here.

\bmhead{Acknowledgments}

Acknowledgments are not compulsory. Where included they should be brief. Grant or contribution numbers may be acknowledged.

Please refer to Journal-level guidance for any specific requirements.

# Declarations {.unnumbered}

Some journals require declarations to be submitted in a standardised format. Please check the Instructions for Authors of the journal to which you are submitting to see if you need to complete this section. If yes, your manuscript must contain the following sections under the heading `Declarations':

* Funding
* Conflict of interest/Competing interests (check journal-specific guidelines for which heading to use)
* Ethics approval
* Consent to participate
* Consent for publication
* Availability of data and materials
* Code availability
* Authors' contributions

\noindent
If any of the sections are not relevant to your manuscript, please include the heading and write `Not applicable' for that section.

::: {.appendices latex=true}

# Section title of first appendix {#secA1}

An appendix contains supplementary information that is not an essential part of the text itself but which may be helpful in providing a more comprehensive understanding of the research problem or it is information that is too cumbersome to be included in the body of the paper.

For submissions to Nature Portfolio Journals please use the heading "Extended Data".  

:::
